Topic Classification of short product Reviews using Label Propagation

### 2012-08-30 docs/paper.tex
Added content for labelPropagation

@@

Since the datasets used in this experiment are real data crawled from twitter and other sources there is a lot of noise in them.\\
Some of the problems are (but not limited) to:\\
\begin{itemize}
	\item Miss spelled words, from typo errors to lack of accents.
	\item Internet Language, replacing some letters for others whose phonetics are similar i.e: ``\textbf{qu}iero" (I want) for ``\textbf{k}iero", abbreviations and expressions (``Jaja'' ``jiji" ... )
	\item Twitter Jargon such as: ``RT:",``@", hashtags and mentions. 
\end{itemize}

The preprocessing done was the following:
\begin{enumerate}
	\item Remove Strange characters, such as hearts, and other unicode characters
	\item Remove some of the Twitter Jargon 
	\item Use \href{http://www.ims.uni-stuttgart.de/projekte/corplex/TreeTagger/}{TreeTagger} ~\cite{Schmid94probabilisticpart-of-speech} for getting the part of speech and the stem of each word in each comment
	\item discard those words that are not adjectives, nouns or verbs
	\item replace each word by its stem in lowercase
	\item remove accents from words
\end{enumerate}

@@

\part*{Feature Generation}
\part*{Structure Learning}

>>>>

~\cite{Speriosu_twitterpolarity} uses Label Propagation for doing Polarity Classification on tweets.\\

@@

The Datasets used in this experiment are actual data crawled from twitter and other sources, therefore there is a lot of noise in them.\\
Some of the problems are (but not limited) to:\\
\begin{itemize}
	\item Miss spelled words, from typo errors to lack of accents.
	\item Internet Language, replacing some letters for others whose phonetics are similar i.e: ``\textbf{qu}iero" (I want) for ``\textbf{k}iero", abbreviations and expressions (``Jaja'' ``jiji" ... )
	\item Twitter Jargon such as: ``RT:",``@"..
\end{itemize}

The pre-processing done was the following:
\begin{enumerate}
	\item Remove Strange characters, such as hearts, and other unicode characters
	\item Remove some of the Twitter Jargon 
	\item Use \href{http://www.ims.uni-stuttgart.de/projekte/corplex/TreeTagger/}{TreeTagger} ~\cite{Schmid94probabilisticpart-of-speech} for getting the part of speech and the stem of each word in each comment
	\item discard those words that are not adjectives, nouns or verbs
	\item replace each word by its stem in lowercase
	\item remove accents from words
\end{enumerate}

When it comes to pre-processing there could be wide number of possible 
tasks that can be done, I try to keep it simple given the time constraints. \\
\\
As a result of this pre-processing each comment is converted into a bag of keywords.\\
This will be later transform into a vector space representation.

%% for future work mention that words like 'camera' that turn out to be good predictor, can be biased by the fact that is misswritten 'camera '  'cmarea'

@@

This Semi-supervised learning graph method was proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
The idea behind Label propagation is similar to K-Neighbors, nevertheless Label propagation make use of the unlabeled data during the training process.\\

This approach maps the data to a graph representation.
In this representation each Arc of the graph will connect two nodes only if the two nodes are similar,
and the weights of the arcs are directly proportional to the similarity of the incident nodes.\\

With respect to our classification task,each node in the graph corresponds to the feature vector of a comment.
The weights of the arcs are given by the cosine distance among the vectors.\\
The final representation is a complete graph.\\
\\
In the LP algorithm, the label information of any
vertex in a graph is propagated to nearby vertices
through weighted edges until a global stable stage is
achieved.~\cite{Chen:2006:REU:1220175.1220192}.
If a weight arc is high, the label will travel easier.\\
\\

\part*{Structure Learning}
A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\

\part*{Feature Generation}
